---
title: "Text as Data project"
author: "Yutong Chen"
output: pdf_document
---

------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=TRUE}
# import libraries
# import libraries
libraries <- c("ldatuning", "topicmodels", "ggplot2", "dplyr", "stm","rjson", "quanteda", "quanteda.corpora","lubridate", "parallel", "doParallel", "tidytext", "stringi", "tidyr","text2vec","bursts","readtext","reshape2","pals","Rtsne", "rsvd" , "geometry" ,"lsa","factoextra","quanteda.textmodels","quanteda.textplots","twitteR","syuzhet","RColorBrewer")
lapply(libraries, require, character.only = TRUE)
```
# topic part

## read in trigram data from the file
```{r echo=TRUE}
read_grams <- function(text1,text2,text3){
  files <- list.files(text1)
  dir <-  paste(text2,files,sep="")    
  n <- length(dir)
  date <- as.Date(gsub(text3, "", files ))
  merge.data <- read.csv(file = dir[1],header=F,col.names = c('gram','counts'))
  merge.data$date <- date[1]
  for (i in 2:n){
     new.data = read.csv(file = dir[i], header=F,col.names = c('gram','counts'))
     new.data$date <- date[i]
     merge.data = rbind(merge.data,new.data)
  }
return(merge.data)
}
bigrams.data <- read_grams('bigrams',"./bigrams/","_top1000bigrams.csv")
grams.data <- read_grams('grams',"./grams/","_top1000terms.csv")
trigrams.data <- read_grams('trigrams',"./trigrams/","_top1000trigrams.csv")
```

## top grams changing over time
```{r echo=TRUE}
require(ggplot2,scales,ggpmisc)

plot_gram_change<- function(data,g){
  temp.data <- data[which(data$gram ==g),]
  theme_set(theme_bw()) # Change the theme to my preference
  my.formula <- y ~ x
  ggplot(aes(x = date, y = counts), data = temp.data) + geom_point()+ geom_smooth(method = "lm", se=FALSE, color="black", formula =   my.formula) +
   ggpmisc::stat_poly_eq(formula = my.formula, 
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE)+scale_y_continuous(labels = scales::comma)+ labs(title = paste("Frequency trend for",g))
}
# coronavirus

plot_gram_change(grams.data,'coronavirus')
plot_gram_change(grams.data,'covid19')
plot_gram_change(grams.data,'wuhanvirus')
plot_gram_change(grams.data,'china')
plot_gram_change(grams.data,'lockdown')
plot_gram_change(grams.data,'quarantine')
plot_gram_change(grams.data,'wearamask')
plot_gram_change(grams.data,'covid')
plot_gram_change(grams.data,'vaccine')


```
## wordcloud
```{r echo=TRUE}
wc_date <- function(data,date,max) {
  temp <- data[which(data$date == date),]
  dev.new(width=100, height=80)
wordcloud::wordcloud(words=temp$gram,freq=temp$counts,max.words=max,random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"))
}

wc_date(bigrams.data,'2021-05-05',300)

bigrams.data[which(bigrams.data$date == date),]


```


```{r echo=TRUE}
merge.data$date =


```
# Vaccine part

```{r echo=TRUE}

# Load data
vaccination_tweets <- read.csv("vaccination_all_tweets.csv", stringsAsFactors = F,encoding = 'UTF-8')

# Create date vectors
class(vaccination_tweets$date)
vaccination_tweets$date2 <- as.Date(vaccination_tweets$date)
vaccination_tweets$month <- month(vaccination_tweets$date2)


# Remove non ASCII characters
vaccination_tweets$text <- stringi::stri_trans_general(vaccination_tweets$text, "latin-ascii")

# Removes solitary letters
vaccination_tweets$text <- gsub(" [A-z] ", " ", vaccination_tweets$text)

# As always we begin with a DFM.
# Create DFM
vaccination_dfm <-dfm(vaccination_tweets$text, stem = F, remove_punct = TRUE, tolower = T, remove_numbers = TRUE, remove = c(stopwords("english"), "http","https","rt", "t.co"))
```

Your written answer goes here.

## most common hashtags

```{r echo=TRUE}
tag_dfm <- dfm_select(vaccination_dfm, pattern = "#*")
toptag <- names(topfeatures(tag_dfm, 150))
toptag[1:20]
```
## Sentiment analysis
```{r echo=TRUE}
vaccination_tweets$sentiment_nrc <- get_nrc_sentiment(vaccination_tweets$text) 
vaccination_tweets$sentiment <- get_sentiment(vaccination_tweets$text) 
unique(vaccination_tweets$hashtags)
vaccination_tweets$hashtags
vaccination_tweets$sentiment_nrc
```


## Group by time
```{r echo=TRUE}

emotion_date <- vaccination_tweets %>%
  group_by(date2) %>%
  summarise(
            anger = sum(ifelse(sentiment_nrc$anger>0,1,0)),
            anticipation = sum(ifelse(sentiment_nrc$anticipation>0,1,0)),
            disgust = sum(ifelse(sentiment_nrc$disgust>0,1,0)),
            fear = sum(ifelse(sentiment_nrc$fear>0,1,0)),
            joy = sum(ifelse(sentiment_nrc$joy>0,1,0)),
            sadness = sum(ifelse(sentiment_nrc$sadness>0,1,0)),
            surprise = sum(ifelse(sentiment_nrc$surprise>0,1,0)),
            trust = sum(ifelse(sentiment_nrc$trust>0,1,0)),
            negative = sum(ifelse(sentiment_nrc$negative>0,1,0)),
            positive = sum(ifelse(sentiment_nrc$positive>0,1,0)))

vizDataFrame <- melt(emotion_date, id.vars = "date2")

# plot topic proportions per month as bar plot
library(RColorBrewer)
ggplot(vizDataFrame, aes(x=date2, y=value, fill=variable)) + 
  geom_area(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Accent"))(10), name = "date") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


```{r echo=TRUE}

emotion_month <- vaccination_tweets %>%
  group_by(month) %>%
  summarise(
            anger = sum(ifelse(sentiment_nrc$anger>0,1,0)),
            anticipation = sum(ifelse(sentiment_nrc$anticipation>0,1,0)),
            disgust = sum(ifelse(sentiment_nrc$disgust>0,1,0)),
            fear = sum(ifelse(sentiment_nrc$fear>0,1,0)),
            joy = sum(ifelse(sentiment_nrc$joy>0,1,0)),
            sadness = sum(ifelse(sentiment_nrc$sadness>0,1,0)),
            surprise = sum(ifelse(sentiment_nrc$surprise>0,1,0)),
            trust = sum(ifelse(sentiment_nrc$trust>0,1,0)),
            negative = sum(ifelse(sentiment_nrc$negative>0,1,0)),
            positive = sum(ifelse(sentiment_nrc$positive>0,1,0)))

vizDataFrame <- melt(emotion_month, id.vars = "month")
emotion_month
# plot topic proportions per month as bar plot
library(RColorBrewer)
ggplot(vizDataFrame, aes(x=month, y=value, fill=variable)) + 
  geom_bar(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = colorRampPalette(brewer.pal(12, "Accent"))(10), name = "month") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


## sentiment - 3
```{r echo=TRUE}
emotion_np <- vaccination_tweets %>%
  group_by(date2) %>%
  summarise(neutral = sum(ifelse(sentiment==0,1,0)),
            negative = sum(ifelse(sentiment<0,1,0)),
            positive = sum(ifelse(sentiment>0,1,0)))
emotion_np_month <- vaccination_tweets %>%
  group_by(month) %>%
  summarise(neutral = sum(ifelse(sentiment==0,1,0)),
            negative = sum(ifelse(sentiment<0,1,0)),
            positive = sum(ifelse(sentiment>0,1,0)))

emotion_np_month
vizDataFrame <- melt(emotion_np, id.vars = "date2")

# plot topic proportions per month as bar plot

ggplot(vizDataFrame, aes(x=date2, y=value, fill=variable)) + 
  geom_line(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = alpha(c('#6495ED','#FFA500','#FF4500'),0.5), name = "sentiment") + 
  theme_set(theme_bw()) 

```

## Group by hashtag
```{r echo=TRUE}

 # Load data
vaccination_tweets_pre <- read.csv("vaccinationtweets.csv", stringsAsFactors = F,encoding = 'UTF-8')


vaccination_tweets_pre$date2 <- as.Date(mdy_hm(vaccination_tweets_pre$date))


vaccination_tweets_pre$sentiment_nrc <- get_nrc_sentiment(vaccination_tweets_pre$text) 
vaccination_tweets_pre$sentiment <- get_sentiment(vaccination_tweets_pre$text) 


emotion_hashtag <- vaccination_tweets_pre %>%
  group_by(hashtags) %>%
  summarise(
            anger = sum(ifelse(sentiment_nrc$anger>0,1,0)),
            anticipation = sum(ifelse(sentiment_nrc$anticipation>0,1,0)),
            disgust = sum(ifelse(sentiment_nrc$disgust>0,1,0)),
            fear = sum(ifelse(sentiment_nrc$fear>0,1,0)),
            joy = sum(ifelse(sentiment_nrc$joy>0,1,0)),
            sadness = sum(ifelse(sentiment_nrc$sadness>0,1,0)),
            surprise = sum(ifelse(sentiment_nrc$surprise>0,1,0)),
            trust = sum(ifelse(sentiment_nrc$trust>0,1,0)),
            negative = sum(ifelse(sentiment_nrc$negative>0,1,0)),
            positive = sum(ifelse(sentiment_nrc$positive>0,1,0)))

vizDataFrame <- melt(emotion_hashtag, id.vars = "hashtags")
emotion_hashtag
# plot topic proportions per month as bar plot

ggplot(vizDataFrame, aes(x=hashtags, y=value, fill=variable)) + 
  geom_bar(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = paste0(alphabet(20), "FF"), name = "hashtags") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

-------------------------------------------------------------------------------
emotion_np <- vaccination_tweets_pre %>%
  group_by(hashtags) %>%
  summarise(neutral = sum(ifelse(sentiment==0,1,0)),
            negative = sum(ifelse(sentiment<0,1,0)),
            positive = sum(ifelse(sentiment>0,1,0)))

emotion_np
/rowSums(emotion_np)

rowSums(emotion_np)
vizDataFrame <- melt(emotion_np, id.vars = "hashtags")
vizDataFrame
# plot topic proportions per month as bar plot

ggplot(vizDataFrame, aes(x=hashtags, y=value, fill=variable)) + 
  geom_bar(stat = "identity") + ylab("proportion") + 
  scale_fill_manual(values = alpha(c('#6495ED','#FFA500','#FF4500'),0.5), name = "sentiment") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


## topic model cutoff data\\

```{r echo=TRUE}

# get subset
first_vaccination_tweets <- vaccination_tweets[which(vaccination_tweets$date2 <= '2021-01-31'),]
second_vaccination_tweets <- vaccination_tweets[which(vaccination_tweets$date2 > '2021-01-31' &vaccination_tweets$date2 <= '2021-02-28'),]
third_vaccination_tweets <- vaccination_tweets[which(vaccination_tweets$date2 > '2021-02-28'),]
```

```{r echo=TRUE}

# fit topic model to each

# Remove non ASCII characters
first_vaccination_tweets$text <- stringi::stri_trans_general(first_vaccination_tweets$text, "latin-ascii")

# Removes solitary letters
first_vaccination_tweets$text <- gsub(" [A-z] ", " ", first_vaccination_tweets$text)

# As always we begin with a DFM.
# Create DFM
first_vaccination_dfm <-dfm(first_vaccination_tweets$text, stem = F, remove_punct = TRUE, tolower = T, remove_numbers = TRUE, remove = c(stopwords("english"), "http","https","rt", "t.co"))


# Set number of topics
k <- 16
# Fit the topic model 
system.time(
  first_vaccination_tm <- LDA(first_vaccination_dfm, chunksize = 50000,k = k, n_iter = 3000, method = "Gibbs",  control = list(seed = 1234)))
# get words for each topic

data.frame(terms(first_vaccination_tm,10))
data.frame(sort(table(topics(first_vaccination_tm,2)),decreasing = TRUE))


```

```{r echo=TRUE}

# fit topic model to each

# Remove non ASCII characters
second_vaccination_tweets$text <- stringi::stri_trans_general(second_vaccination_tweets$text, "latin-ascii")

# Removes solitary letters
second_vaccination_tweets$text <- gsub(" [A-z] ", " ", second_vaccination_tweets$text)

# As always we begin with a DFM.
# Create DFM
second_vaccination_dfm <-dfm(second_vaccination_tweets$text, stem = F, remove_punct = TRUE, tolower = T, remove_numbers = TRUE, remove = c(stopwords("english"), "http","https","rt", "t.co"))


# Set number of topics
k <- 16
# Fit the topic model 
system.time(
  second_vaccination_tm <- LDA(second_vaccination_dfm, k = k, n_iter = 3000, method = "Gibbs", chunk_size = 50000, control = list(seed = 1234)))
# get words for each topic
data.frame(terms(second_vaccination_tm,20))
data.frame(sort(table(topics(second_vaccination_tm,2)),decreasing = TRUE))

```
```{r echo=TRUE}

# fit topic model to each

# Remove non ASCII characters
third_vaccination_tweets$text <- stringi::stri_trans_general(third_vaccination_tweets$text, "latin-ascii")

# Removes solitary letters
third_vaccination_tweets$text <- gsub(" [A-z] ", " ", third_vaccination_tweets$text)

# As always we begin with a DFM.
# Create DFM
third_vaccination_dfm <-dfm(third_vaccination_tweets$text, stem = F, remove_punct = TRUE, tolower = T, remove_numbers = TRUE, remove = c(stopwords("english"), "http","https","rt", "t.co"))


# Set number of topics
k <- 16
# Fit the topic model 
system.time(
  third_vaccination_tm <- LDA(third_vaccination_dfm, k = k, n_iter = 3000, method = "Gibbs", chunk_size = 50000, control = list(seed = 1234)))
# get words for each topic
data.frame(terms(third_vaccination_tm,20))
data.frame(sort(table(topics(third_vaccination_tm,2)),decreasing = TRUE))
```



```{r echo=TRUE}

```


```{r echo=TRUE}
summary <- vaccination_tweets %>%
  group_by(date2) %>%
  summarise(
            mean = round(mean(sentiment), 2),
            num_tweets = n())

summary %>%
  ggplot(aes(date2, mean)) +
    geom_line(size = 1) + 
    scale_x_continuous(name = "\nTime", breaks = NULL) +
    scale_y_continuous(name = "Sentiment\n") 



```


